Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-30 paper_comparison/paper_comparison/paper_comparison.Rmd
refine the start of the experimental design

Three experiments are conducted to investigate the difference between conventional hypothesis testing and visual inference in the application of linear regression diagnostics. The experiment I has ideal scenario for conventional testing, where the visual test is not expected to outperform the conventional test. Meanwhile, the experiment II is a scenario where the conventional test is an approximate test, in which the visual test may have a chance to match the performance of the conventional test. The experiment III is designed for collecting human responses to null lineups such that the parameter $\alpha$ in Equation \ref{eq:pvalue-beta-binomial} can be estimated. Overall, we plan to collect `r vi_survey  %>% filter(!attention_check) %>% nrow()` evaluations on `r vi_survey  %>% filter(!attention_check) %>% pull(unique_lineup_id) %>% unique() %>% length()` unique lineups performed by `r vi_survey  %>% filter(!attention_check) %>% count(exp, set) %>% nrow()` subjects throughout three experiments.

@@

Two types of departures, namely non-linearity and heteroskedasticity, are considered with the corresponding data generating process being designed for experiment I and II.

>>>>

Three experiments are conducted to investigate the difference between conventional hypothesis testing and visual inference in the application of linear regression diagnostics. Two types of departures, namely non-linearity and heteroskedasticity, are considered with the corresponding data generating process being designed for experiment I and II. The experiment III is designed for collecting human responses to null lineups such that the parameter $\alpha$ in Equation \ref{eq:pvalue-beta-binomial} can be estimated. Overall, we plan to collect `r vi_survey  %>% filter(!attention_check) %>% nrow()` evaluations on `r vi_survey  %>% filter(!attention_check) %>% pull(unique_lineup_id) %>% unique() %>% length()` unique lineups performed by `r vi_survey  %>% filter(!attention_check) %>% count(exp, set) %>% nrow()` subjects throughout three experiments.

@@

### 2023-01-30 paper_comparison/paper_comparison/paper_comparison.tex
refine the start of the experimental design

Three experiments are conducted to investigate the difference between
conventional hypothesis testing and visual inference in the application
of linear regression diagnostics. The experiment I has ideal scenario
for conventional testing, where the visual test is not expected to
outperform the conventional test. Meanwhile, the experiment II is a
scenario where the conventional test is an approximate test, in which
the visual test may have a chance to match the performance of the
conventional test. The experiment III is designed for collecting human
responses to null lineups such that the parameter \(\alpha\) in Equation
\ref{eq:pvalue-beta-binomial} can be estimated. Overall, we plan to
collect 7974 evaluations on 1152 unique lineups performed by 443
subjects throughout three experiments.

>>>>

Three experiments are conducted to investigate the difference between
conventional hypothesis testing and visual inference in the application
of linear regression diagnostics. Two types of departures, namely
non-linearity and heteroskedasticity, are considered with the
corresponding data generating process being designed for experiment I
and II. The experiment III is designed for collecting human responses to
null lineups such that the parameter \(\alpha\) in Equation
\ref{eq:pvalue-beta-binomial} can be estimated. Overall, we plan to
collect 7974 evaluations on 1152 unique lineups performed by 443
subjects throughout three experiments.
